---
title: "Linear Regression: Predicting the survival of Lung Cancers."
output: html_notebook
---
## Goal of the project

The idea behind our model is to predict the overall survival length of adults suffering from a lung cancer. Our model is fed only with clinical data prior to the eventual death of the patient. 

## Mandatory Imports

ggplot: ploting library
dplyr: to pipe with the `%>%` symbol.

```{r}
#Import libraries
library(ggplot2)
library(dplyr, warn.conflicts = FALSE)
library(moments)

# Import the data
cancers = read.csv("cancer.csv", sep=',')
cancers = na.omit(cancers)
#cancers$sex = factor(cancers$sex, labels=c("Male", "Female"))
#cancers$status = factor(cancers$status)
```
## Descriptive analysis
### Means
```{r}
summarise_all(cancers, funs(mean))
```
### Standard deviation
```{r}
summarise_all(cancers, funs(sd))
```

### Skewness
```{r}
summarise_all(cancers, funs(skewness))
```
### Kurtosis

```{r}
summarise_all(cancers, funs(kurtosis))
```

### Box plots

```{r}
ggplot(stack(cancers), aes(x = ind, y = values)) + geom_boxplot()
ggplot(stack(cancers[c("inst", "status", "age", "sex", "ph.ecog", "ph.karno", "pat.karno", "wt.loss")]), aes(x=ind, y=values)) + geom_boxplot()
ggplot(stack(cancers[c("status", "sex", "ph.ecog")]), aes(x=ind, y=values)) + geom_boxplot()
```

## Exploratory Data Analysis

```{r}
ggplot(cancers, aes(y=time, x=ph.ecog)) + geom_point(alpha=0.2) + geom_smooth(method='lm') + scale_y_log10()
```
```{r}
ggplot(cancers, aes(y=time, x=pat.karno)) + geom_point(alpha=0.2) + geom_smooth(method='lm') + scale_y_log10()

cancers %>%
  summarize(
    N= n(),
    r=cor(log(time), pat.karno)
  )
```
```{r}
ggplot(cancers, aes(y=time, x=meal.cal)) + geom_point() + geom_smooth(method='lm') + scale_y_log10()
```
```{r}
ggplot(cancers, aes(y=time, x=wt.loss, col=sex)) + geom_point() + geom_smooth(method='lm') + scale_y_log10()
```

```{r}

```

